The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-01-21 paper/ms.tex
Wrote initial draft of observations/data reduction section

>>>>

The stellar sample for this survey is defined by the following criteria:

\begin{itemize}
\item $V < 6$
\item $v\sin{i} > 80 \mathrm{km\ s}^{-1}$
\item Spectral Type A or B with the following additional constraints
\begin{itemize}
  \item Main Sequence
  \item No spectral peculiarities except for `n', which denotes broad lines.
\end{itemize}
\end{itemize}

The first two criteria are to ensure that the direct spectral detection technique (Section \ref{sec:companions}) both works and is well-calibrated. The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time. It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}. Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, it does not actually remove very many stars from the sample. Finally we only include normal, main sequence stars in the sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.

We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey. We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for most southern targets. This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber. The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders. We therefore bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.

For the northern targets, we use a combination of the High Resolution Spectrograph \citep[HRS,][]{HRS} on the Hobby Eberly Telescope, and the Tull coud\'e \citep[TS23,][]{TS23} and IGRINS \citep{IGRINS} spectrographs, both on the 2.7m Harlan J. Smith Telescope. All three northern instruments are at McDonald Observatory. For the HRS, we use the $R = 60000$ setting with a $2''$ fiber, and with wavelength coverage from 410-780 nm. We bias-correct, flat-field, and extract the spectra using an IRAF pipeline. The HRS spectra are wavelength-calibrated using a Th-Ar lamp observed immediately before or after the science observations.

For the TS23, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm. We reduce the data using an IRAF pipeline very similar to the one we use for the HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.

IGRINS only has one setting with $R = 40000$. It has complete wavelength coverage from 1475-2480 nm, except for where telluric absorption is almost $100\%$ from 1810 - 1930 nm. Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}. The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines.

After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}. We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal. The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines. For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to. For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.

TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
